As an output of this analysis a list of \glspl{appr} has been derived.
Each project was part of the Research and Innovation Action funding scheme and focused on \gls{bim} as the main topic.
In the following we report a short list of the main \glspl{appr}: the project description (\gls{appr}1), objectives (\gls{appr}2), field of science, programmes, topics, proposal call, funding scheme, and keywords (\gls{appr}3).
In addition, there are the most important details concerning the coordinating organisation (\gls{appr}4) of the project, and all the organisations participating (\gls{appr}5) in that project.
Each organisation presents secondary information such as postal address, location (\gls{appr}6), and main type of activity.
The available information only concerns organisations.
However, for the recommendation of collaborators it is important to also know which people from the relevant organisations are involved in the projects, therefore we considered it as an additional requirement (\gls{appr}7).
Table \ref{tab:application-requirements} shows the list of \glspl{appr} and their corresponding description.

\begin{table}[htbp]
    \centering
    \scriptsize
    \begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}p{2cm}|X|}
      \hline
      \textbf{Application Requirement} & \textbf{Description}\\
        \hline
        \gls{appr}1 & Project Description \\
        \gls{appr}2 & Objectives \\
        \gls{appr}3 & Field of Science, Programmes, Topics, Proposal Call, Funding Scheme, Keywords \\
        \gls{appr}4 & Coordinating Organisation \\
        \gls{appr}5 & Participating Organisations \\
        \gls{appr}6 & Postal Address, Location, Main Type of Activity \\
        \gls{appr}7 & People involved in the projects \\
        \hline
    \end{tabularx}
    \caption{List of \acrfullpl{appr} and their corresponding description}
    \label{tab:application-requirements}
\end{table}
        