\chapter{Introduction}\label{chap:intro}

This chapter presents the foundation of the thesis including the background, challenges, and goals of the study.
It begins with the Background (Sec. \ref{sec:background}), which provides an overview of research collaboration, its importance in advancing scientific discovery, and the role of digital tools and recommender systems in facilitating such collaborations.
The chapter then moves to the Problem Statement (Sec. \ref{sec:problem-statement}), highlighting the limitations of traditional approaches and existing \gls{ai} methods in identifying potential research collaborators, such as their lack of interpretability, contextual understanding, and ability to generalize across diverse scenarios.
Sec. \ref{sec:thesis-statement} defines the Thesis Statement, which outlines the proposed solution: a recommender system integrating knowledge graphs and large language models to deliver accurate, explainable, and context-aware recommendations.
The Research Gap (Sec. \ref{sec:research-gap}) identifies shortcomings in current methods, emphasizing the unexplored potential of combining knowledge graphs with retrieval-augmented large language models to enhance precision and explainability.
The chapter also illustrates Research Questions (Sec. \ref{sec:research-questions}) to guide the investigation and concludes with a Thesis Structure (Sec. \ref{sec:thesis-structure}), offering a roadmap for the subsequent chapters of the document.

\section{Background}\label{sec:background}
Research collaboration is the process where researchers from various fields, institutions, or disciplines work together to achieve shared scientific objectives (\cite{KATZ19971}).
The exponential growth of academic research in various fields has increased the need for effective collaboration between researchers (\cite{Adams2012, Vermeulen2017}).
Research collaborations are commonly used in areas such as medicine, engineering, social sciences, and environmental studies, where diverse expertise is often required to tackle intricate problems.
According to \cite{Mei2021}, these collaborations are vital for addressing complex, multidisciplinary challenges, advancing knowledge, and accelerating innovation.
They typically take the form of joint publications, shared research grants, co-developed methodologies, and interdisciplinary studies.
Their importance is underscored by their ability to share resources and knowledge and foster innovation, making them key factors in scientific progress.

Traditional approaches to collaboration often rely on professional networking through conferences, workshops, and institutional partnerships (\cite{KATZ19971}).
These methods have proven effective in facilitating connections, but are often constrained by geographic and logistical limitations.
Digital tools, such as ResearchGate\footnote{\url{https://www.researchgate.net}}, Academia.edu\footnote{\url{https://www.academia.edu}}, Google Scholar\footnote{\url{https://scholar.google.com}} and LinkedIn\footnote{\url{https://www.linkedin.com}}, have expanded the reach of collaborations, allowing researchers to network online, share results, and identify potential collaborators around the world.
However, these platforms focus primarily on social connectivity rather than intelligent matchmaking based on complementary expertise or shared goals.

Recommender systems (\cite{Lu2012}) are \gls{ai} algorithms that make suggestions and recommendations about the most relevant items for a particular user.
Nowadays, they are widely used in commercial contexts such as e-commerce and streaming platforms and have shown significant potential to address the challenge of matching individuals with relevant objects or entities (\cite{Hussien2021}).

In recent years, area of \gls{ai} such as \gls{ml} and \gls{dl} algorithms,  \glspl{kg}, and \glspl{llm} have emerged as powerful tools for developing intelligent and interpretable recommendation systems (\cite{Zhao2024}).
\glspl{kg} enable the representation of structured information about entities and their relationships, providing a basis for reasoning and generating insights.
At the same time, \glspl{llm} have demonstrated remarkable abilities to process and understand complex textual information. 

The Semantic Web, an extension of the World Wide Web for enhancing the current web plays a crucial role in this context.
By embedding structured, machine-readable data into web resources, the Semantic Web allows information to be interconnected and queried seamlessly across diverse datasets.
Standards such as the \gls{rdf} (\cite{Cyganiak14RCA}) and \gls{owl} (\cite{Deborah2004}) form the foundation of the Semantic Web, enabling interoperability and integration of data from various sources.
These capabilities are particularly valuable for applications requiring complex reasoning and decision-making.

The combination of advanced \gls{ai} methodologies with Semantic Web technologies has opened new possibilities for enhancing recommender systems.
By leveraging the structured, interconnected data of the Semantic Web alongside the predictive power of \gls{ai} algorithms, these systems can deliver more accurate, relevant, and context-aware recommendations.
This not only improves the effectiveness of recommender systems but also expands their potential to address the sophisticated requirements of users in academic and scientific collaboration settings.
%
\section{Problem Statement}\label{sec:problem-statement}

Research collaboration is an essential part of modern scientific progress, but it presents many challenges that make it difficult to be effective.
A significant problem comes from disciplinary and cognitive differences: collaborators from different fields often struggle to reconcile conflicting methodologies, priorities, and theoretical perspectives.
Communication barriers further make these challenges more difficult, as insufficient or ineffective exchanges between team members can lead to misunderstandings and a lack of cohesion.
Inconsistent levels of commitment within teams often create imbalances, with some researchers prioritizing their personal goals over collective ones, thus straining trust and productivity.
In addition, disputes over equity, such as work distribution, authorship, and access to resources, can lead to employee dissatisfaction and resentment.
Ineffective leadership and management practices, such as overregulation or lack of flexibility, often fail to adequately address these problems or may even intensify them.
Cultural and social differences, including variations in organizational norms, gender, or cultural background, while potentially enriching collaboration, can also generate friction if not managed inclusively.


\glspl{dnn} have achieved remarkable progress in enhancing recommender systems by modeling user-item interactions and incorporating textual side information.
These systems are very good at capturing patterns and preferences from large datasets, often leading to state-of-the-art performance in recommendation tasks.
However, despite these advancements, \gls{dnn}-based recommender systems have several limitations:
\begin{enumerate}
    \item Understanding users' interests: \glspl{dnn} often struggle to effectively comprehend users' intricate and evolving interests, particularly in highly dynamic domains such as academic research.
    \item Capturing textual side information: while incorporating textual data such as abstracts, keywords, or titles, \glspl{dnn} may fail to adequately integrate this information into the recommendation process due to limitations in contextual understanding.
	\item Generalization challenges: \gls{dnn}-based systems face difficulties in generalizing across various seen and unseen recommendation scenarios, reducing their applicability in real-world settings with sparse or incomplete data.
	\item Lack of interpretability: \glspl{dnn} are often criticized for their black-box nature, making it challenging to provide meaningful explanations for recommendations and undermining user trust in the system.
\end{enumerate}
		

These challenges underscore the need for more sophisticated methods that integrate domain-specific knowledge, facilitate reasoning, and provide interpretable recommendations in specific contexts, such as research collaboration.
%
\section{Thesis Statement}\label{sec:thesis-statement}

This thesis proposes the design and development of a recommendation system that leverages the power of \glspl{kg} and \glspl{llm} to provide accurate and explainable recommendations for identifying potential research collaborators.
By integrating \glspl{kg}, which provide a structured and interconnected representation of domain-specific information, with the contextual understanding and generative capabilities of \glspl{llm}, the system aims to address key challenges of research collaboration recommendations.
These include understanding complex academic relationships, the research consortia and projects and areas of interest of researchers, and explaining the motivations behind recommendations.
The proposed system leverage the strengths of both technologies to retrieve and analyze relevant academic data, dynamically adapt to user preferences, and provide personalized and well-justified recommendations, thus enhancing the process of finding and connecting with suitable research collaborators.
%
\section{Research Gap}\label{sec:research-gap}
\input{01_Chapters/literature-review/research-gap.tex}
%
\section{Research Questions}\label{sec:research-questions}
The main \gls{rq} is derived from the thesis statement and guides the investigation:

\textit{How can a \gls{kg} and \gls{llm}-based approach enhance the process of suggesting research collaborators for researchers?}

To address this question, the following subquestions are explored:
\begin{itemize}
	\item Awareness of the problem: \textit{how can research-related data (e.g., publications, topics, affiliations) be effectively modeled into a \gls{kg} to capture relationships among researchers?}
	\item Suggestions: \textit{How can a \gls{kg} and \gls{llm}-based system be designed to efficiently retrieve relevant information from large, heterogeneous data sources to support personalized recommendations?}
	\item Implementation: \textit{How can the system generate human-readable explanations for its research collaborator recommendations using the \gls{kg} and \gls{llm} outputs?}
\end{itemize}

%\begin{itemize}
%    \item Knowledge Representation: \textit{how can research-related data (e.g., publications, topics, affiliations) be effectively modeled into a \gls{kg} to capture relationships among researchers?}
%	\item Information Retrieval: \textit{What techniques can be employed to efficiently retrieve relevant information from large, heterogeneous data sources to support personalized recommendations?}
%	\item Explainability: \textit{How can the system generate human-readable explanations for its recommendations using the \gls{kg} and \gls{llm} outputs?}
%	\item Evaluation: \textit{What metrics and evaluation frameworks are suitable to assess the accuracy, usability, and satisfaction of the proposed system?}
%\end{itemize}

By addressing these questions, this thesis aims to contribute to the field of intelligent recommender systems and facilitate impactful research collaborations.

\section{Thesis Structure}\label{sec:thesis-structure}
TODO
%Chapter \ref{chap:literature-review} provides an overview of the relevant literature on \glspl{kg}, \glspl{gnn}, and \glspl{llm}, as well as related work on research collaboration recommendation systems;
%Chapter \ref{chap:research-method} outlines the methodology used to design and implement the proposed system;
%Finally \ref{chap:conclusion} concludes the thesis and discusses potential future research directions.

