\ackPage{
    In this final part, I would like to dedicate a few words to all those who, throughout my journey, have supported, helped, and encouraged me, making it possible for me to reach this point and complete my thesis.
    
    My deepest thanks go to my supervisors, Prof.~Michela Quadrini and Dr.~Emanuele Laurenzi, for their constant availability, immense patience, and invaluable advice.
    I am truly grateful for the knowledge they shared and the guidance they provided throughout every stage of this project.
    Thank you for your professionalism, for proposing such an engaging and rewarding thesis topic, and for the trust and freedom you gave me along the way.

    I would also like to express my heartfelt thanks to all those who have supported by me over the past few years.
    Their advice, guidance, and moments of lightheartedness have helped me through some of the most significant periods of my life.
    
    A sincere thank you to my colleagues and fellow students, who know just as well as me do how passionate, engaging, and challenging this journey has been.
    Thank you for sharing with me both the hard work and the enjoyable moments.
    
    To my closest friends, thank you for all the experiences I've shared and for always being by my side.

    A special thank you goes to my family for their unwavering support through their advice, affection, and encouragement, and for standing by me both emotionally and financially throughout my academic journey.

    And lastly, thanks to the music that kept me alive during the long days and late nights, making even the most intense moments lighter.

    My deepest thanks to all of you.
}