\chapter{Literature Review}\label{chap:literature-review}
As part of the problem awareness phase, the literature review summarises the relevant scientific literature related to the thesis' topics.
It lays the groundwork for answering to the research questions.
Initially, Sec.~\ref{sec:research-collaboration} discusses the definition and importance of research collaboration and methods for finding potential research collaborators.
Sec.~\ref{sec:knowledge-graphs} provides an overview of knowledge graphs, from theoretical aspects to real-world applications.
Existing knowledge graphs and ontologies in the research field are also described.
Sec.~\ref{sec:large-language-models} briefly provides an overview of \glspl{llm}, applications of these technologies with their advantages and limitations.
Sec.~\ref{sec:retrieval-augmented-generation} explains \gls{rag} models, their architecture, and applications.
Sec.~\ref{sec:recommender-systems} explains recommender systems, particularly existing recommendation systems in the research domain and \gls{rag}-based recommendation systems.
Finally, Sec.~\ref{sec:literature-requirements} lists the literature requirements that will be addressed in this thesis.
%
\section{Research Collaboration}\label{sec:research-collaboration}
\input{chapters/literature-review/research-collaboration.tex}
%
\section{Knowledge Graphs}\label{sec:knowledge-graphs}
\input{chapters/literature-review/knowledge-graphs.tex}
%
\section{Large Language Models}\label{sec:large-language-models}
\input{chapters/literature-review/large-language-models.tex}
%
\section{Retrieval-Augmented Generation}\label{sec:retrieval-augmented-generation}
\input{chapters/literature-review/rag.tex}
%
\section{Recommender Systems}\label{sec:recommender-systems}
\input{chapters/literature-review/recommender-systems.tex}
%
\section{Literature Requirements}\label{sec:literature-requirements}
\input{chapters/literature-review/literature-requirements.tex}
