The following \glspl{lr} were selected from the relevant works in the literature.
Several \glspl{kg} exist in the research and scholarly fields, but no work uses them in the European research domain.
The definition of an ontology and/or use of a \gls{kg} in this domain is necessary in order to allow semantic representation of European projects (\gls{lr}1).
Among current research recommender systems, some exploit various filtering approaches including \gls{cbf}.
Generating \gls{cbf} recommendation could be quite efficient (\gls{lr}2), for example if based on a project description or abstract, recommend potential collaborators, who have collaborated on a project with that description similar to the one specified.
Unfortunately, some \gls{dl}-based recommender systems need data training to perform the assigned task.
In some cases it may also be necessary to retrain the model.
In these cases, generating recommendations without performing either training or other techniques such as fine-tuning helps to save computational power (\gls{lr}3).
Regarding the hop reasoning perspective, retrieving relevant information dynamically, using models such as \glspl{gnn}, can require high computations on graphs, especially on large graphs (\gls{lr}4).
Table~\ref{tab:literature-requirements} shows the list of \glspl{lr} and their corresponding description.

\begin{table}[htbp]
    \centering
    \scriptsize
    \begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}p{2cm}|X|}
      \hline
      \textbf{Literature Requirement} & \textbf{Description}\\
        \hline
        \gls{lr}1 & Definition of an ontology and/or use of a \gls{kg} in the European research domain \\
        \gls{lr}2 & Exploitation of \gls{cbf} in research recommender systems \\
        \gls{lr}3 & Generation of recommendations without training or fine-tuning \\
        \gls{lr}4 & High computational power for dynamic retrieval of relevant information using \glspl{gnn} \\
        \hline
    \end{tabularx}
    \caption{List of \acrfullpl{lr} and their corresponding description}
    \label{tab:literature-requirements}
\end{table}